# Methods {#methods}

```{r methods_init, include=FALSE}
library(knitr)
library(tidyverse)
source('analysis/qualtrics.R')
```

## Participants

`r nrow(mod_data)` undergraduate students from Reed College in Portland, Oregon participated in an online survey about "attitudes towards gendered pronouns." Participants were recruited through online advertisements and posters around campus. Notably, this sample is around one-third of the undergraduate student body. Data collection was conducted over a two month period, starting in February 2020. It should also be noted that the global pandemic that occurred in early 2020 shortened our opportunity to collect data. 

Participants of all genders were recruited, including cisgender participants. @tateIntegratingStudyTransgender2014 advocate for the integration of cisgender and non-cisgender gender research into one body of research on gender identity development. They push back on the common assumption that cisgender people do not undergo a period of self-reflection and self-categorization in the maturation of their gender identity. Furthermore, by not excluding cisgender participants from the study, we allowed freer self-categorization e.g. for the inclusion of people who identified as cisgender and non-binary. 

## Transgender Inclusive Behavior Scale (TIBS)

The Transgender Inclusive Behavior Scale was developed by @kattariDevelopmentValidationTransgender2018 to provide a measure for actions and modes of communication that are inclusive and supportive of transgender people. The TIBS was developed for participants of all gender identities—not exclusively cisgender people. 

The TIBS includes a broad array of trans affirming behaviors. This includes several items such as sharing their own pronouns and asking for others', educating themselves on local policies that may affect transgender people, and speaking out against transphobia in their communities. 

Responses were collected as five-point likert scales ranging from "Never" to "Always." Each participant's responses were added to produce a score that generally represented how many inclusive behaviors one performed.

While selecting our measures, we elected to use the TIBS in lieu of a measure such as the transphobia scale developed by @nagoshiGenderDifferencesCorrelates2008. This was done to generally frame the study as positive and affirming for transgender people. Administering questions about transphobic attitudes to transgender people who are the victims of transphobia and transmisogynistic violence could have been significantly more distressing than asking about affirming and supportive behaviors. Essentially, the TIBS was included as a proxy for how intentionally participants supported and affirmed their transgender peers. 

An added potential benefit to administering the TIBS to cisgender participants is that it potentially includes actions that cisgender people had not yet considered doing to support their transgender peers. As data collection progressed, the author received several messages from participants reporting that they had never considered some of the actions, like ensuring that gender-neutral bathrooms were available at events that they organized. 

## Transgender Congruence Scale (TCS)

The Transgender Congruence Scale was developed by @kozeeMeasuringTransgenderIndividuals2012 to provide a measure for how transgender people feel "genuine, authentic, and comfortable with their gender identity and external appearance." The TCS was developed for transgender participants. However, we elected to administer the TCS to cisgender participants as well. This was done to avoid presuming that cisgender people have a purely passive relationship with their gender, as is advocated for by @tateIntegratingStudyTransgender2014. 

Responses were collected as five-point likert scales ranging from "Strongly Disagree" to "Strongly Agree" Each participant's responses were added to produce a score that generally represented how congruent one felt with one's gender identity. The TCS consists of 12 items that include relationships between the participant's gender identity, their physical appearance and presentation, their body, and their social experience with gender. 

## Gendered Pronoun Attitude Survey (GPAS)

The GPAS was developed as a broad survey of undergraduate students' relationships and experiences with gendered pronouns. Many items were phrased similarly to questions from the TCS. However, as this is a very novel area of study, the author created most of them herself in consultation with other gender-diverse peers. 

Responses were collected as five-point likert scales ranging from "Strongly Disagree" to "Strongly Agree." In the first block of questions, participants were asked to report their experiences from the past two weeks. This was done to reflect the Transgender Congruence Scale (TCS) by @kozeeMeasuringTransgenderIndividuals2012. The TCS asked participants to reflect on their relationship with gender in the past two weeks. 
```{r, echo = FALSE}
data.frame(question = c(
  "I feel comfortable sharing my pronouns in most settings.",
  "I feel comfortable sharing my pronouns in non-academic settings in the Reed community.",
  "I feel comfortable sharing my pronouns in classes at Reed.",
  "I want to share my pronouns in most settings.",
  "I want to share my pronouns in non- academic settings in the Reed community.",
  "I want to share my pronouns in classes at Reed.",
  "I feel more comfortable sharing my pronouns if I am with people who may have similar gender identities to me.",
  "I feel more comfortable introducing myself with my pronouns if someone else does first.",
  "I feel more comfortable introducing myself with my pronouns in class if the professor does first.",
  "I am concerned that sharing my pronouns will draw unwanted attention to myself in most settings.",
  "I am concerned that sharing my pronouns will draw unwanted attention to myself in non-academic settings in the Reed community",
  "I am concerned that sharing my pronouns will draw unwanted attention to myself in class at Reed.",
  "I feel that the gender that people perceive me as and my pronouns are consistent with one another.",
  "I feel that my internal gender identity and pronouns are consistent with one another.",
  "I feel that my pronouns represent my gender identity well.",
  "If I don’t tell people what my pronouns are, they will misgender me.",
  "I don’t need to tell people what my pronouns are, because they usually assume correctly.",
  "I feel like people understand me better when I share my pronouns."
  )) %>%
  kable(
    col.names = c("Item Description"),
    caption = "Pronoun attitude questionnaire items: past 2 weeks"
  )
```
In the second block of questions, participants were asked to reflect on their experience across their entire time at Reed. These questions drew on participants extended experience at the college and reflection on each semester. 
```{r, echo = FALSE}
data.frame(question = c(
  "In classes at Reed, professors usually introduce themselves with their pronouns",
  "In classes at Reed, students usually introduce themselves with their pronouns",
  "Enough is being done at Reed to support people who have the same gender as me."
  )) %>%
  kable(
    col.names = c("Item Description"),
    caption = "Pronoun attitude questionnaire items: entire time at Reed"
  )
```