% This is the Reed College LaTeX thesis template. Most of the work
% for the document class was done by Sam Noble (SN), as well as this
% template. Later comments etc. by Ben Salzberg (BTS). Additional
% restructuring and APA support by Jess Youngberg (JY).
% Your comments and suggestions are more than welcome; please email
% them to cus@reed.edu
%
% See http://web.reed.edu/cis/help/latex.html for help. There are a
% great bunch of help pages there, with notes on
% getting started, bibtex, etc. Go there and read it if you're not
% already familiar with LaTeX.
%
% Any line that starts with a percent symbol is a comment.
% They won't show up in the document, and are useful for notes
% to yourself and explaining commands.
% Commenting also removes a line from the document;
% very handy for troubleshooting problems. -BTS

% As far as I know, this follows the requirements laid out in
% the 2002-2003 Senior Handbook. Ask a librarian to check the
% document before binding. -SN

%%
%% Preamble
%%
% \documentclass{<something>} must begin each LaTeX document
\documentclass[12pt,twoside]{reedthesis}
% Packages are extensions to the basic LaTeX functions. Whatever you
% want to typeset, there is probably a package out there for it.
% Chemistry (chemtex), screenplays, you name it.
% Check out CTAN to see: http://www.ctan.org/
%%
\usepackage{graphicx,latexsym}
\usepackage{amsmath}
\usepackage{amssymb,amsthm}
\usepackage{longtable,booktabs,setspace}
\usepackage{chemarr} %% Useful for one reaction arrow, useless if you're not a chem major
\usepackage[hyphens]{url}
% Added by CII
\usepackage{hyperref}
\usepackage{lmodern}
\usepackage{float}
\floatplacement{figure}{H}
% End of CII addition
\usepackage{rotating}

% Next line commented out by CII
%%% \usepackage{natbib}
% Comment out the natbib line above and uncomment the following two lines to use the new
% biblatex-chicago style, for Chicago A. Also make some changes at the end where the
% bibliography is included.
%\usepackage{biblatex-chicago}
%\bibliography{thesis}


% Added by CII (Thanks, Hadley!)
% Use ref for internal links
\renewcommand{\hyperref}[2][???]{\autoref{#1}}
\def\chapterautorefname{Chapter}
\def\sectionautorefname{Section}
\def\subsectionautorefname{Subsection}
% End of CII addition

% Added by CII
\usepackage{caption}
\captionsetup{width=5in}
% End of CII addition

% \usepackage{times} % other fonts are available like times, bookman, charter, palatino

% Syntax highlighting #22

% To pass between YAML and LaTeX the dollar signs are added by CII
\title{Pronouns Good or Bad: Attitudes and Relationships with Gendered Pronouns
in Gender-Diverse Undergraduates}
\author{Jade Fung}
% The month and year that you submit your FINAL draft TO THE LIBRARY (May or December)
\date{May 2020}
\division{Philosophy, Religion, Psychology, and Linguistics}
\advisor{Vasiliy Safin}
\institution{Reed College}
\degree{Bachelor of Arts}
%If you have two advisors for some reason, you can use the following
% Uncommented out by CII
% End of CII addition

%%% Remember to use the correct department!
\department{Psychology}
% if you're writing a thesis in an interdisciplinary major,
% uncomment the line below and change the text as appropriate.
% check the Senior Handbook if unsure.
%\thedivisionof{The Established Interdisciplinary Committee for}
% if you want the approval page to say "Approved for the Committee",
% uncomment the next line
%\approvedforthe{Committee}

% Added by CII
%%% Copied from knitr
%% maxwidth is the original width if it's less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

%Added by @MyKo101, code provided by @GerbrichFerdinands

\renewcommand{\contentsname}{Table of Contents}
% End of CII addition

\setlength{\parskip}{0pt}

% Added by CII

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\Acknowledgements{
I want to thank a few people.
}

\Dedication{
This thesis is dedicated to he/him lesbians.
}

\Preface{
This is an example of a thesis setup to use the reed thesis document
class (for LaTeX) and the R bookdown package, in general.
}

\Abstract{
\chapter{Abstract}\label{abstract}

The preface pretty much says it all. \par

Second paragraph of abstract starts here.
}

% End of CII addition
%%
%% End Preamble
%%
%
\begin{document}

% Everything below added by CII
  \maketitle

\frontmatter % this stuff will be roman-numbered
\pagestyle{empty} % this removes page numbers from the frontmatter
  \begin{acknowledgements}
    I want to thank a few people.
  \end{acknowledgements}
  \begin{preface}
    This is an example of a thesis setup to use the reed thesis document
    class (for LaTeX) and the R bookdown package, in general.
  \end{preface}
  \hypersetup{linkcolor=black}
  \setcounter{tocdepth}{2}
  \tableofcontents

  \listoftables

  \listoffigures
  \begin{abstract}
    \chapter{Abstract}\label{abstract}
    
    The preface pretty much says it all. \par
    
    Second paragraph of abstract starts here.
  \end{abstract}
  \begin{dedication}
    This thesis is dedicated to he/him lesbians.
  \end{dedication}
\mainmatter % here the regular arabic numbering starts
\pagestyle{fancyplain} % turns page numbering back on

\chapter*{Introduction}\label{introduction}
\addcontentsline{toc}{chapter}{Introduction}

Pronouns are small words used in place of nouns in sentences
(``Pronoun,'' 2020). Gendered pronouns are a type of pronoun that
identifies the subject's gender when used (``Preferred gender pronoun,''
2019). For example, in the sentence ``she walks the dog,'' she is the
third person pronoun that replaces the subject's name. In English, the
most common pronouns are ``she,'' ``they,'' and ``he.'' It is important
to note that ``they'' is widely recognized as both a singular and plural
pronoun (``They,'' 2019).

Gendered pronouns are especially important for transgender and
non-binary individuals, since their apperance and gender may not match
cisnormative expectations.

\chapter{Literature Review}\label{litreview}

Gendered pronouns.

\chapter{Methods}\label{methods}

\emph{Participants}

477 undergraduate students from Reed College in Portland, Oregon
participated in an online survey about ``attitudes towards gendered
pronouns.'' Participants were recruited through online advertisements
and posters around campus. Notably, this sample is around one-third of
the undergraduate student body. Data colleciton was conducted over a two
month period, starting in Febuary 2020. It should be noted that the
global pandemic that occured in early 2020 shortened our opportunity to
collect data.

\chapter{Results}\label{results}

\section{Experiences with
Misgendering}\label{experiences-with-misgendering}

Similar to McLemore (2015), we had partcipants report how frequently
they were misgendered and how stigmatized misgendering made them feel.
However, unlike McLemore (2015), we administered these questions to
cisgender people as well. Independent t-tests were used to compare the
cisgender (\emph{N} = 276) and non-cisgender participants (\emph{N} =
156). Non-cisgender participants (\emph{M} = 3.28, \emph{SD} = 0.96)
reported being misgendered more frequently than cisgender participants
(\emph{M} = 1.45, \emph{SD} = 0.7), \emph{t}(231) = 21.6, \emph{p} =
\textless{} 0.001. Non-cisgender participants (\emph{M} = 3.15,
\emph{SD} = 1.3) also reported feeling more stigmatized when misgendered
than than cisgender participants (\emph{M} = 1.59, \emph{SD} = 1.01),
\emph{t}(261) = 12.9, \emph{p} = \textless{} 0.001.
\begin{table}

\caption{\label{tab:unnamed-chunk-1}Misgendering frequency for non-cisgender and cisgender participants}
\centering
\begin{tabular}[t]{l|r|r}
\hline
“How often do people ‘misgender’ you?” & Non-cisgender (\%) & Cisgender (\%)\\
\hline
Never & 6.4 & 68.8\\
\hline
Rarely & 14.0 & 24.9\\
\hline
Sometimes & 30.6 & 4.7\\
\hline
Often & 44.6 & 1.3\\
\hline
Always & 4.5 & 0.3\\
\hline
\end{tabular}
\end{table}
\begin{table}

\caption{\label{tab:unnamed-chunk-2}Felt stigma when misgendered for non-cisgender and cisgender participants}
\centering
\begin{tabular}[t]{l|r|r}
\hline
“I feel stigmatized (looked down upon)when I am misgendered.” & Non-cisgender (\%) & Cisgender (\%)\\
\hline
Not at all & 12.2 & 68.5\\
\hline
Slightly & 20.5 & 12.0\\
\hline
Somewhat & 28.2 & 13.4\\
\hline
Considerably & 18.6 & 4.0\\
\hline
Very & 20.5 & 2.2\\
\hline
\end{tabular}
\end{table}
Pearson's Chi-squared tests were used to compare the misgendering
frequency observed in McLemore (2015) to the non-cisgender participants
in the present study. There were significant differences when compared
to both the study 1 population, \emph{X2} (4, \emph{N} = 544) = 13.54,
\emph{p} = 0.01, and the study 2 population, \emph{X2} (4, \emph{N} =
582) = 11.41, \emph{p} = 0.02.

McLemore (2015) performed a one-way ANOVA ``to compare differences among
three gender groups (transgender men, transgender women, and
genderqueer)'' in misgendering frequency and felt stigma when
misgendered. Because I took a different approach to collecting
gender-related demographic data, I elected to perform a factorial ANOVA
comparing endorsement of several endorsed identities on misgendering
frequency and felt stigma.

There were multiple significant effects of identity endorsement on
misgendering frequency. Cisgender, \emph{F}(1, 464) = 702.04, \emph{p} =
\textless{} 0.001, transgender, \emph{F}(1, 464) = 21.3, \emph{p} =
\textless{} 0.001, and non-binary identity, \emph{F}(1, 464) = 40.59,
\emph{p} = \textless{} 0.001, all demonstrated significant effects.
There was no significant effect in women (\emph{p} = 0.11) or men
(\emph{p} = 0.08) alone. However, there was a significant effect in
transgender women, \emph{F}(1, 464) = 11.76, \emph{p} = \textless{}
0.001. There was not a significant effect in transgender men (\emph{p} =
0.37). There was also a significant effect in non-binary women ,
\emph{F}(1, 464) = 11.76, \emph{p} = 0.004, but not in non-binary men
(\emph{p} = 0.296).

There were also multiple sigificant effects of identity endorsement on
felt stigma when misgendered. Cisgender, \emph{F}(1, 422) = 210.75,
\emph{p} = \textless{} 0.001, and transgender , \emph{F}(1, 422) =
39.81, \emph{p} = \textless{} 0.001, identities demonstrated significant
effects. However, non-binary (\emph{p} = 0.15) identity did not show a
significant effect. Neither men (\emph{p} = 0.51) nor women (\emph{p} =
0.38) alone showed significant effects, nor did trans women (\emph{p} =
0.69). However, trans men, \emph{F}(1, 422) = 7.41, \emph{p} =
\textless{} 0.001, demonstrated a significant effect. Neither non-binary
men (\emph{p} = 0.77) nor non-binary women (\emph{p} = 0.43)
demonstrated a significant effect.

Unlike McLemore (2015), I also collected participants pronouns. This
allowed me to perform a factorial ANOVA with a follow-up Tukey test to
examine pronouns, independent of gender, had an effect on misgendering
frequency.

\section{Gender Congruence}\label{gender-congruence}

Kozee, Tylka, \& Bauerband (2012) developed the TCS (Transgender
Congruence Scale) to measure transgender individuals' relationship and
comfort between their inner gender identity, physical appearance, and
social experience of gender. Tate, Youssef, \& Bettergarcia (2014)
advocate for integrating the study of transgender and cisgender
populations to practice a more cohesive study of gender experinces. So,
I administered the TCS to cisgender participants as well.

Unlike Kozee et al. (2012), I collected gender-related demographic data
by asking participants to write in their gender identity. I
qualatatively coded themes from the write-in gender question. Then I
administered the following yes/no questions: ``Are you cisgender?,''
``Are you transgender?,'' and ``Is your gender non-binary?'' Answering
yes on one question did not force the participants to answer no on
others---this treated gender identity as a collection of seperate,
related labels that participants may or may not identify with
simaltaneously.
\begin{verbatim}
  cis_n
1   477
\end{verbatim}
Overall, \texttt{r} participants identified as cisgender, \texttt{r}
identified as transgender, and \texttt{r} identified their gender as
non-binary.

Non-cisgender participants demonstrated lower scores on the TCS than

\chapter{Discussion}\label{discussion}

So, we found some gendered pronouns.

\appendix

\backmatter

\chapter*{References}\label{references}
\addcontentsline{toc}{chapter}{References}

\markboth{References}{References}

\noindent

\setlength{\parindent}{-0.20in} \setlength{\leftskip}{0.20in}
\setlength{\parskip}{8pt}

\hypertarget{refs}{}
\hypertarget{ref-kozee_measuring_2012}{}
Kozee, H. B., Tylka, T. L., \& Bauerband, L. A. (2012). Measuring
Transgender Individuals' Comfort With Gender Identity and Appearance:
Development and Validation of the Transgender Congruence Scale.
\emph{Psychology of Women Quarterly}, \emph{36}(2), 179--196.
\url{http://doi.org/10.1177/0361684312442161}

\hypertarget{ref-mclemore_experiences_2015}{}
McLemore, K. A. (2015). Experiences with Misgendering: Identity
Misclassification of Transgender Spectrum Individuals. \emph{Self and
Identity}, \emph{14}(1), 51--74.
\url{http://doi.org/10.1080/15298868.2014.950691}

\hypertarget{ref-noauthor_preferred_2019}{}
Preferred gender pronoun. (2019, November). \emph{Wikipedia}. Retrieved
from
\url{https://en.wikipedia.org/w/index.php?title=Preferred_gender_pronoun\&oldid=925883384}

\hypertarget{ref-noauthor_pronoun_2020}{}
Pronoun. (2020). \emph{Mirriam-Webster}. Retrieved from
\url{https://www.merriam-webster.com/dictionary/pronoun}

\hypertarget{ref-tate_integrating_2014}{}
Tate, C. C., Youssef, C. P., \& Bettergarcia, J. N. (2014). Integrating
the Study of Transgender Spectrum and Cisgender Experiences of
Self-Categorization from a Personality Perspective. \emph{Review of
General Psychology}, \emph{18}(4), 302--312.
\url{http://doi.org/10.1037/gpr0000019}

\hypertarget{ref-noauthor_they_2019}{}
They. (2019). \emph{Merriam-Webster.com}. Retrieved from
\url{https://www.merriam-webster.com/dictionary/they}


% Index?

\end{document}
